### 2015-07-10 narrative/intro.tex
added some text about performance bounds. can someone with storage experience clean this up?

One of our  research objectives is to understand how the
storage system can interact with the middleware   so
that the data with the highest utility is kept on the fastest layers of the
storage system for as long as specified. We need to maintain 
QoS and therefore, be able to provide fuzzy estimates of the time it will take to write/read data from
the different layers to inform any migration/eviction decisions, and it
is also critical that the storage system can manage (discover and retrieve) the data across all of the
layers automatically, without user intervention. 
%We will use learning techniques to automatically migrate data
%sub-objects across the hierarchy as well as to eventually evict data which is
%large and has very low utility.

>>>>

One of our  research objectives is to understand how the
storage system can interact with the middleware   so
that the data with the highest utility is kept on the fastest layers of the
storage system for as long as specified. We need to maintain 
QoS and therefore, be able to provide fuzzy estimates of the time it will take to write/read data from
the different layers to inform any migration/eviction decisions, and it
is also critical that the storage system can manage (discover and retrieve) the data across all of the
layers automatically, without user intervention. 
Central to our approach is that the storage system needs to define bounds of time estimates
(min time, max time), and as our system evolves, we want to allow plug-ins which can help
reduce the range of the bounds, and furthermore, with optimizations we would like to minimize 
the times for both reading and writing. Thus, we want predictable performance, and methods
which can obtain better performance bounds in time.

%We will use learning techniques to automatically migrate data
%sub-objects across the hierarchy as well as to eventually evict data which is
%large and has very low utility.
